### 2021-11-03 Final Doc/Chapters/Chapter1.tex
Final Docs Updated

\begin{figure}[H]
\centering
\includegraphics[scale=1.5]{Figures/swot}
\caption{Swot Analysis of the Project}
\end{figure}

@@

\section{Provisional Chapter Division}
This document will contain a bulk of the final project documentation and the associated literature study. It will be divided into separate chapters which are listed below with a brief description of the respective content.
\\\\
\textbf{Chapter 1: Introduction} \\	
The problem that is being researched, the qualities of games needed for use in education, is discussed in Chapter 1. Information on the background of this problem, similar research and the research contribution will be discussed. Furthermore, the aim of the study in addition to the planned method of conduct will be discussed.
\\\\
\textbf{Chapter 2: Literature Study} \\
Chapter 2 will discuss the impact of games both in early development and in general in more detail, the accessibility of games as well as a focus on games being used in learning. It will attempt to find what qualities and principles work best to make a game a suitable means of learning.
\\\\
\textbf{Chapter 3: Development of Accompanying Artefact} \\
The accompanying artefact that will be developed as a part of the study will be discussed along with the development process of the artefact.
\\\\
\textbf{Chapter 4: Review of Collected Data} \\
The means of data collection, processing and analysis will be discussed in this chapter along with the results of this data. As this project pertains to the application of knowledge towards an artefact, this section will mostly discuss the underlying principles and qualities that make for a game to be used in a learning capacity.
\pagebreak
\textbf{Chapter 5: Discussion on Results} \\
A discussion on the results obtained will be presented in this chapter. This chapter will focus more on the application of the acquired knowledge and principles towards the development of the artefact.
\\\\
\textbf{Chapter 6: Conclusion} \\
The contents and results of the study will be briefly discussed and reiterated in an overview.
\\\\
\textbf{Reference List} \\
Contains all literary works referenced in the project.

>>>>

\begin{figure}[H]
\centering
\includegraphics[scale=2]{Figures/swot}
\caption{Swot Analysis of the Project}
\end{figure}

@@

\section{Provisional Chapter Division}
This document will contain a bulk of the final project documentation and the associated literature study. It will be divided into separate chapters which are listed below with a brief description of the respective content.
\\\\
\indent \textbf{Chapter 1: Introduction} \\	
The problem that is being researched, the qualities of games needed for use in education, is discussed in Chapter 1. Information on the background of this problem, similar research and the research contribution will be discussed. Furthermore, the aim of the study in addition to the planned method of conduct will be discussed.
\\
\indent \textbf{Chapter 2: Literature Study} \\
Chapter 2 will discuss the impact of games both in early development and in general in more detail, the accessibility of games as well as a focus on games being used in learning. It will attempt to find what qualities and principles work best to make a game a suitable means of learning.
\\
\indent \textbf{Chapter 3: Development of Artefact and Article} \\
The accompanying artefact that will be developed as a part of the study will be discussed along with the development process of the artefact.
\\
\indent \textbf{Chapter 4: Results} \\
A discussion on the results obtained will be presented in this chapter. This chapter will focus more on the application of the acquired knowledge and principles towards the development of the artefact.
\\
\indent \textbf{Chapter 5: Reflection} \\
The contents and results of the study will be briefly discussed and reiterated in an overview in addition to a brief discussion on how the project could possibly progress.
\\
\indent \textbf{Reference List} \\
Contains all literary works referenced in the project.

### 2021-11-03 Final Doc/Chapters/Chapter3.tex
Added and Updated Final Doc Latex
Final Docs Updated

% Chapter 1

\chapter{Introduction} % Main chapter title

\label{Chapter1} % For referencing the chapter elsewhere, use \ref{Chapter1}

%----------------------------------------------------------------------------------------

% Define some commands to keep the formatting separated from the content 
\newcommand{\keyword}[1]{\textbf{#1}}
\newcommand{\tabhead}[1]{\textbf{#1}}
\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\file}[1]{\texttt{\bfseries#1}}
\newcommand{\option}[1]{\texttt{\itshape#1}}

%----------------------------------------------------------------------------------------

\section{Project Description}

\section{Project Contents}
\subsection{Problem Description and Background}
\subsection{Overview of Related Literature}
\subsection{Research Question and Expected Outcomes}

\section{Aims and Objectives of Project}

\section{Procedures and Methods of Investigation}
\subsection{Research Paradigm and Methodology Used}
\subsection{Collection of Data}
\subsection{Development of Artefact}
\subsection{Integration with Other Projects}

\section{Approach to Project Management and Project Plan}
\subsection{Provisional Project Plan}
\subsection{Scope}
\subsection{Contributions of Each Group Member}

\section{Development Platform, Resources and Environments}
\subsection{Development Platform}
\subsection{Resources}
\subsection{Environments}

\section{Ethical Implications of Project}

\section{Provisional Chapter Division}

>>>>

% Chapter 3

\chapter{Development of Artefact and Article} % Main chapter title

\label{Chapter3} % For referencing the chapter elsewhere, use \ref{Chapter1}

This chapter describes the artefact that was developed in a group effort as well as the process followed for the writing of the academic article.

\section{Description of Artefact}
This research project was split into two main aspects: 
\begin{enumerate}
\item An individual research study into a chosen topic \textit{(this being the qualities needed for a computer game to be used in education)}
\item A group effort to develop a digital computer game.
\end{enumerate}

\noindent For the first aspect of this project, the resulting outcome was an academic article titled, \textit{"Linking Gamification, Ludology and Pedagogy: How to Use Serious Games for Various Knowledge Domains"}. As stipulated in the title, the fields of gamification, ludology and pedagogy were the focus of this research aspect of the project. In this article, the question posed by this project is again reiterated and sequentially answered. The article is attached to this document under Appendix  \ref{AppendixC}. 
\\\\
The artefact accompanying this research project is a digital computer came which was developed as part of a group effort as mentioned previously. While this artefact is separate from the individual research studies conducted by its' group members, it may have been influenced by the topics being researched. The artefact is titled \textit{"Puzzle Ball: Spherical Shadows"} and is further categorised as a 3D puzzle platformer with aspects of action gameplay played in first person. A playable version of the artefact is available on the website itch.io website\footnote{\url{https://josh-scg.itch.io/puzzle-ball-spherical-shadows}} and the source code of the artefact is available on GitHub\footnote{\url{https://github.com/GCWehmeyer/Spherical_Shadows}}$^{,}$\footnote{\url{https://github.com/Josh-SCG/Spherical_Shadows}}

\section{Artefact Life Cycle Followed and its Different Phases}
% Briefly provide general background on the life cycle that was followed and why it is appropriate to this artefact.

\section{Description of the Development of the Artefact}
%Comprehensive report on the way in which each phase of the life cycle was applied in the development of this artefact.
